\documentclass{scrreprt}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage[final]{hcar}

%include polycode.fmt

\begin{document}

\begin{hcarentry}{pulp}
\report{Daniel Wagner}
\status{Not yet released}
\participants{Daniel Wagner, Michael Greenberg}
\makeheader

Anybody who has used \LaTeX\ knows that it is a fantastic tool for
typesetting; but its error reporting leaves much to be desired. Even simple
documents that use a handful of packages can produce hundreds of lines of
uninteresting output on a successful run. Reviewing this output manually to
pick out the interesting parts---like errors and warnings---is a serious
chore. Sometimes, even when you have found something of interest in the
output, one must refer to the more complete log file written to disk to
discover what really went wrong, and where; and these can easily be
thousands of lines of uninteresting output to wade through. Moreover, as a
document passes through the writing lifecycle, different \emph{kinds} of
messages are of interest. For example, in early drafts, when text is still
undergoing major changes, it can be a waste of time to fret about underfull
boxes or bad hyphenations, though these become important as the document
enters its later stages. Unfortunately, \LaTeX\ itself has few knobs to
adjust what messages are reported.

Pulp addresses these concerns. It includes a parser for \LaTeX\ log files
and a small but expressive configuration language for identifying which
messages are of interest. The program then shows only the interesting parts
of the log file. A typical run of pulp after successfully building a
document produces no output; this makes it very easy to spot when something
has gone wrong.

Next time you want to produce a great paper, process your log with pulp!

\paragraph*{Features}
\begin{compactitem}
	\item \LaTeX\ log parser with special-case support for many popular
		packages and classes, including article, babel, beamer, fancyvrb,
		fp, geometry, graphicx, KOMA-Script, llncs, memoir, natbib, nowidow,
		pdfpages, prooftree, scrlfile, xparse, xypic
	\item Expressive configuration language based on zeroth-order logic with
		atoms for error level, error content, reporting package, and more
	\item Uniform error reporting format
		\begin{compactitem}
			\item File and line number location information
			\item Line-number guessing heuristic for errors that do not
				report line information
			\item Clear delineation of multi-line errors
		\end{compactitem}
	\item Integration with latexmk
	\item Rudimentary Windows support
\end{compactitem}

% What's following are suggestions for the content of an entry.
%
% (WHAT IS IT?)
%
% (WHAT IS ITS STATUS? / WHAT HAS HAPPENED SINCE LAST TIME?)
%
% (CAN OTHERS GET IT?)
%
% (WHAT ARE THE IMMEDIATE PLANS?)

\FurtherReading
  \url{http://github.com/dmwit/pulp}
\end{hcarentry}

\end{document}
